Learning a functional distance between organizations with unsupervised embeddings of scientific mobility

### 2020-08-03 paper/current/main.tex
edits s1 fig

We model co-occurences $T_{ij$} for organizations $i$, and $j$, often referred to as flux, using the gravity law of mobility~\autocite{zipf1946gravity}.
The gravity law of mobility loosely derives from the physical law of gravity, in which the attraction between two objects is a function of their mass and the distance between them.
This formulation and variants have proven useful for modeling and predicting many kinds of mobility~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity}.
In the gravity law of mobility, the \textit{expected flux}, $\hat{T_{ij}}$ between two organizations $i$ and $j$ is defined as,

@@

%
% Figure - publications over time
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Descriptive/pubs_over_time.pdf}
	\caption{
		\textbf{Publications over time.}
		\textbf{a.}
		The number of papers published by mobile authors has been steadily increasing from 2008 to 2017, with a small decrease in 2018,  likely an artifact of the Web of Science indexing process.
		Lines correspond to publications by mobile authors (org, purple), by authors with affiliations in at least two cities (blue), at least two regions (green), and at least two countries (yellow).
		There is no evidence of major changes in the publication patterns of mobile authors during this time period.
		\textbf{b.}
		Lines correspond to the proportion of publications classified as Biology and Health (black), Physics and Engineering (purple), Life and Earth Science (magenta), Social Science and Humanities (orange), and Math and Computer Science (yellow).
		The rate of publication in Biology and Health has leveled since about 2013, whereas the rate of publication in other fields has steadily increased.
		\textbf{c.}
		Despite increasing absolute counts, the percentage of mobile scholars, and those with at least two city, regional, or country affiliations, as a proportion of all publications, has decreased over time.
		\textbf{d.}
		The proportion of authors' publications across fields has largely remained steady.
		Biology and Health Science has comprised the majority of publications across nearly all years but has steadily declined in proportion.
		However, the proportion of Social Science and Humanities publications has been steadily increasing.
	}
	\label{fig:supp:pubs_over_time}
\end{figure}

>>>>

We model co-occurences $T_{ij}$ for organizations $i$, and $j$, often referred to as flux, using the gravity law of mobility~\autocite{zipf1946gravity}.
The gravity law of mobility loosely derives from the physical law of gravity, in which the attraction between two objects is a function of their mass and the distance between them.
This formulation and variants have proven useful for modeling and predicting many kinds of mobility~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity}.
In the gravity law of mobility, the \textit{expected flux}, $\hat{T_{ij}}$ between two organizations $i$ and $j$ is defined as,

@@

%
% Figure - publications over time
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Descriptive/pubs_over_time.pdf}
	\caption{
		\textbf{Publications over time.}
		\textbf{a.}
		The number of papers published by mobile authors has been steadily increasing from 2008 to 2017, with a small decrease in 2018,  which may be due to an artifact of the Web of Science indexing process.
		Lines correspond to publications by mobile authors, by authors with affiliations in at least two cities, at least two regions, and at least two countries.
		We did not find major changes in the publication patterns of mobile authors during this time period.
		\textbf{b.}
		Lines correspond to the proportion of publications classified as Biology and Health (black), Physics and Engineering (purple), Life and Earth Science (magenta), Social Science and Humanities (orange), and Math and Computer Science (yellow).
		The rate of publication in Biology and Health has leveled since about 2013, whereas the rate of publication in other fields has steadily increased.
		\textbf{c.}
		While the absolute count of publications has increased, the percentage of mobile scholars, and those with affiliations in at least least two cities, regions, or countries, as a proportion of all publications, has decreased over time.
		\textbf{d.}
		The proportion of authors' publications across fields has largely remained steady.
		Biology and Health Science has comprised the majority of publications across nearly all years but has steadily declined in proportion.
		However, the proportion of Social Science and Humanities publications has been steadily increasing.
	}
	\label{fig:supp:pubs_over_time}
\end{figure}
